
**Setup**

Working Directory
```{r setup}
knitr::opts_knit$set(root.dir = "C:/Users/Harrison Kirby/Desktop/GLP/CCU18")
```

Libraries
```{r libraries, message = FALSE}
library(lubridate)
library(ggthemes)
library(classInt)
library(showtext)
library(feather)
library(survey)
library(tidyverse)
library(magrittr)
library(reshape2)
```

Add functions
```{r}
insurance_time <- function(starting.year=2006){
  wd <- getwd()
  directory <- "Health/sahie_2008/"
  file_names <- list.files(directory)
  n<-length(file_names)
  y<-starting.year
  for (i in 1:n){
    file_path <- paste(directory, file_names[i], sep = "")
    data<-read_csv(file_path, skip=79)
    
    if(y > 2007){ data <- data %>% select(-X26) }
    
    data$statefips <- as.character(data$statefips)
    data$countyfips <- as.character(data$countyfips)
    
    data$statefips <- if_else( nchar(data$statefips) < 2, paste0("0",data$statefips), data$statefips)
    data$countyfips <- if_else( nchar(data$countyfips) < 3, paste0("0",data$countyfips), data$countyfips)
    data$countyfips <- if_else( nchar(data$countyfips) < 3, paste0("0",data$countyfips), data$countyfips)
    
    data$FIPS <- as.numeric(paste0(data$statefips, data$countyfips))
    all.peers <-subset(data, data$FIPS == 1073 |data$FIPS == 37119
                       |data$FIPS == 39061 |data$FIPS == 39049
                       |data$FIPS == 26081 |data$FIPS == 37081
                       |data$FIPS == 45045 |data$FIPS == 18097
                       |data$FIPS == 29095 |data$FIPS == 47093
                       |data$FIPS == 21111 |data$FIPS == 47157
                       |data$FIPS == 47037 |data$FIPS == 40109
                       |data$FIPS == 31055 |data$FIPS == 29189
                       |data$FIPS == 29510
                       |data$FIPS == 40143 |data$FIPS == 39113
                       |data$FIPS == 12031 |data$FIPS == 37183
                       |data$FIPS == 51760)
    
    all.peers$year<-y
    y<-y+1
    
    if(i==1){
     df<-all.peers 
    }
    else{
      names(all.peers)<-names(df)
      df<-rbind(df, all.peers)
    }
  }
  df
}


pull_peers_MSA<-function(data){
  all.peers <- filter(data, data$MSA %in% c("24340", "41180", "36420", "46140", "24860", "28940", "13820", "26900", "31140", "28140", "36540", "24660", "16740", "18140", "17140", "34980", "32820", "27260", "39580", "19380", "40060"))
  
  all.peers$baseline <- 1
  all.peers$current  <- 1
  
  all.peers$baseline[all.peers$MSA == 24340 | all.peers$MSA == 41180
                     |all.peers$MSA == 36420 | all.peers$MSA == 46140
                     |all.peers$MSA == 24860 | all.peers$MSA == 28940] <-0
  
  all.peers$current[all.peers$MSA == 27260 | all.peers$MSA == 39580
                    |all.peers$MSA == 19380 | all.peers$MSA == 40060] <-0
  all.peers
}

pull_peers_FIPS <- function(dat){
  all.peers <- subset(dat, dat$FIPS == 1073 | dat$FIPS == 37119
                      |dat$FIPS == 39061 |dat$FIPS == 39049
                      |dat$FIPS == 26081 |dat$FIPS == 37081
                      |dat$FIPS == 45045 |dat$FIPS == 18097
                      |dat$FIPS == 29095 |dat$FIPS == 47093
                      |dat$FIPS == 21111 |dat$FIPS == 47157
                      |dat$FIPS == 47037 |dat$FIPS == 40109
                      |dat$FIPS == 31055 |dat$FIPS == 29189
                      |dat$FIPS == 29510 |dat$FIPS == 40143
                      |dat$FIPS == 12031 |dat$FIPS == 37183
                      |dat$FIPS == 39113 |dat$FIPS == 51760
                      |dat$FIPS == "01073" | dat$FIPS == "MERGED")
  all.peers$baseline <- 1
  all.peers$current <- 1
  all.peers$baseline[all.peers$FIPS==26081|all.peers$FIPS==29189
                     |all.peers$FIPS==29510|all.peers$FIPS==40109
                     |all.peers$FIPS==40143|all.peers$FIPS==45045
                     |all.peers$FIPS==47093|all.peers$FIPS=="MERGED"]<-0
  all.peers$current[all.peers$FIPS== 12031|all.peers$FIPS==37183|
                      all.peers$FIPS==39113|all.peers$FIPS==51760]<-0
  all.peers
}
```

# Education : Bachelor Degree Attainment ages 25-64

## Ranking


## Trendline by Race: W/B/H

## Map of BA degrees in Lou

## Change --  poverty vs. nonpoverty

##Other:

### Associate's Ranking

### Associate's by race trendline

### Young adult degrees (assoc or bach)

### Education pipeline

# Jobs: median earnings

## Ranking

## Trendline by race

## Map

## change: high wage jobs

##Other:

### Earnings gap

### Distribution of job across the city/payroll + jobs by zip

### Unemployment trendline by race

### Working poverty

### Income inequality

# Health: health outcomes index

## Ranking

## Trendline by race

## Map of life expectancy

## Change; % of children in poverty

## Other:

### Health insurance by race

### Health insurance by income quartiles (demonstrate impact of expanded Medicaid)

# QOP

## Ranking: homeownership

## Trendline: homeownership by race

## Map: homeownership or burdened households

## change: home values by areas

## Other

### % of MSA in core county

### Housing stock $ by race

### Segregation = % race by % area

### Brain drain migration figures

### Disconnected youth figures


